Hierarchical Dispatching and Overriding

### 2017-06-18 Aplas17/sections/Introduction.tex
Terminology.

In contrast with the diamond inheritance, a second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
methods that do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but they just happen to have same names (and
signatures).
A simple example of this situation are two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicted methods have very different meanings and do not share a
common parent. We call such a case ``\textit{triangle inheritance}''.
\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}

@@

Some other workarounds or approaches include delegation, and
renaming/exclusion in the trait model. Yet they still have various
drawbacks as we will discuss in Section~\ref{sec:overview}. Closest to our work
are mechanisms available in C++ and C\# that allow for two
unintentionally conflicted methods to coexist in a class. Among them
C++ is a representative that accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching}. However, C++ has
limited support for virtual methods with unintentional conflicts, and
it will often throw errors when composing them. This is again
unsatisfactory because virtual methods are pervasive in OOP and used 
for code reuse and extensibility. A problem with the C++ approach is
that programmers can only use either static or dynamic dispatching separately, but dealing
with unintentional method conflicts seems to require a combination of both.

>>>>

In contrast with the diamond inheritance, a second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
methods that do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but they just happen to have same names (and
signatures).
A simple example of this situation are two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicting methods have very different meanings and do not share a
common parent. We call such a case ``\textit{triangle inheritance}''.
\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}

@@

Some other workarounds or approaches include delegation, and
renaming/exclusion in the trait model. Yet they still have various
drawbacks as we will discuss in Section~\ref{sec:overview}. Closest to our work
are mechanisms available in C++ and C\# that allow for two
unintentionally conflicting methods to coexist in a class. Among them
C++ is a representative that accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching}. However, C++ has
limited support for virtual methods with unintentional conflicts, and
it will often throw errors when composing them. This is again
unsatisfactory because virtual methods are pervasive in OOP and used 
for code reuse and extensibility. A problem with the C++ approach is
that programmers can only use either static or dynamic dispatching separately, but dealing
with unintentional method conflicts seems to require a combination of both.

### 2017-06-18 Aplas17/sections/Overview.tex
Terminology.

\noindent\textbf{Potential Fixes} There are several workarounds that come to our mind:
\begin{itemize}
  \item \textbf{I. Delegation.} As an alternative to multiple inheritance,
  delegation can be used by introducing two fields with
  \lstinline|Drawable| type and \lstinline|Deck| type,
  respectively. This avoids method conflicts. Nevertheless, it is known
  that using delegation makes it hard to correctly maintain
  self-references \haoyuan{need to cite} in an extensible system [], and also
  introduces a lot of boilerplate code.
  \item \textbf{II. Refactor Drawable and/or Deck to rename the methods.} If
  the code for \lstinline|Drawable| or \lstinline|Deck| are available
  then it may be possible to rename one of the \lstinline|draw|
  methods. However this approach is non-modular, as it requires 
  modifying existing code, and may not be possible if code is unavailable.
  \item \textbf{III. Method exclusion/renaming in traits.} Some trait models
  support method exclusion/renaming. Those features
  provided can eliminate conflicts, although most
  programming languages do not support them. In a traditional OO system,
  they can break the subtyping. Moreover, in
  contrast with exclusion, renaming can indeed preserve both conflicted
  behaviours, however, it is cumbersome in practice, as introducing new
  names can affect other code blocks.
  \item \textbf{IV. Static dispatch.} Some other languages like C++ have
  direct support for the triangle inheritance. While conflicting methods are
  both preserved, the ambiguity of method call is resolved by static dispatch.
  Qualified names are used to specify the branch to give the right implementation.
\end{itemize}

>>>>

\noindent\textbf{Potential Fixes} There are several workarounds that come to our mind:
\begin{itemize}
  \item \textbf{I. Delegation.} As an alternative to multiple inheritance,
  delegation can be used by introducing two fields with
  \lstinline|Drawable| type and \lstinline|Deck| type,
  respectively. This avoids method conflicts. Nevertheless, it is known
  that using delegation makes it hard to correctly maintain
  self-references \haoyuan{need to cite} in an extensible system [], and also
  introduces a lot of boilerplate code.
  \item \textbf{II. Refactor Drawable and/or Deck to rename the methods.} If
  the code for \lstinline|Drawable| or \lstinline|Deck| are available
  then it may be possible to rename one of the \lstinline|draw|
  methods. However this approach is non-modular, as it requires 
  modifying existing code, and may not be possible if code is unavailable.
  \item \textbf{III. Method exclusion/renaming in traits.} Some trait models
  support method exclusion/renaming. Those features
  provided can eliminate conflicts, although most
  programming languages do not support them. In a traditional OO system,
  they can break the subtyping. Moreover, in
  contrast with exclusion, renaming can indeed preserve both conflicting
  behaviours, however, it is cumbersome in practice, as introducing new
  names can affect other code blocks.
  \item \textbf{IV. Static dispatch.} Some other languages like C++ have
  direct support for the triangle inheritance. While conflicting methods are
  both preserved, the ambiguity of method call is resolved by static dispatch.
  Qualified names are used to specify the branch to give the right implementation.
\end{itemize}
